Carbonate reanalysis

### 2021-06-20 inst/rmd/carbonate_reanalysis.Rmd
Add latest wheel

```{r}
library(tidyverse)
library(here)
library(amstools)
library(HybridGIS)
```

```{r}
wheels <- c("020521", "030421", "040121", "041521", "051421", "052621", "061121")
files <- here("data", paste0("USAMS", wheels, "R.txt"))
dates <- as.Date(c("2021-02-05", "2021-03-05", "2021-04-09", "2021-04-16", "2021-05-14", "2021-05-28", "2021-06-11"))
stds <- list(c(5,8), NULL, c(26,37), NULL, c(10,15,65,70), NULL, NULL)
blanks <- list(7, c(7,8), c(28,29,30), c(27,28,29), c(20,35,50), NULL, NULL)
outliers <- list(NULL, tibble(pos = c(6, 8, 8, 8), meas = c(18, 1, 2, 3)),
                 tibble(pos = c(28,29), meas=c(1, 1)),
                 NULL,
                 tibble(pos=10, meas=1),
                 tibble(pos=c(8,9,13), meas=c(6,1,1)),
                 tibble(pos=c(4,5,5,6,7,8,15), meas=c(1,1,4,10,3,3,2)))

@@

cons_df %>% 
  select(wheel, pos, sample_name, fm_consensus, fm_corr, sig_fm_corr, Fm_diff, sigma) %>% 
  arrange(desc(Fm_diff))
```

>>>>

```{r}
library(tidyverse)
library(here)
library(amstools)
library(HybridGIS)

theme_set(theme_bw())
options(digits = 3)
options(scipen = 4)
```

```{r}
wheels <- c("020521", "030421", "040121", "041521", "051421", "052621", "061121", "061821")
files <- here("data", paste0("USAMS", wheels, "R.txt"))
dates <- as.Date(c("2021-02-05", "2021-03-05", "2021-04-09", "2021-04-16", "2021-05-14", "2021-05-28", "2021-06-11", "2021-06-18"))
stds <- list(c(5,8), NULL, c(26,37), NULL, c(10,15,65,70), NULL, NULL, NULL)
blanks <- list(7, c(7,8), c(28,29,30), c(27,28,29), c(20,35,50), NULL, NULL, 23)
outliers <- list(NULL, tibble(pos = c(6, 8, 8, 8), meas = c(18, 1, 2, 3)),
                 tibble(pos = c(28,29), meas=c(1, 1)),
                 NULL,
                 tibble(pos=10, meas=1),
                 tibble(pos=c(8,9,13), meas=c(6,1,1)),
                 tibble(pos=c(4,5,5,6,7,8,15), meas=c(1,1,4,10,3,3,2)),
                 NULL)

@@

cons_df %>% 
  select(wheel, pos, sample_name, fm_consensus, fm_corr, sig_fm_corr, Fm_diff, sigma) %>% 
  filter(wheel == "USAMS061821")
  arrange(desc(Fm_diff))
```
